Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-15 introduction.tex
Updates from Overleaf

With the newly developed techniques, we revisit the classical verification of quantum computation problem from both a philosophical and a practical point of view. 
Our first observation is that the sampling version of $\BQP$ (e.g., as formulated by Aaronson~\cite{aaronson_2013})

>>>>

With the newly developed techniques, we revisit the classical verification of quantum computation problem from both a philosophical and a practical point of view. 
Our first observation is that the sampling version of $\BQP$ (e.g., as formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem. 
Philosophically, experiments of quantum mechanics usually generate samples and statistical information, which is well demonstrated in the famous double-split

### 2020-04-15 qpip0.tex
Updates from Overleaf

\begin{lemma}[binding property of $\PiNaive$]
\label{lem:naive-qpip0-binding}
	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
	Under the QLWE assumption, if $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
	\Ethan{Wrong assumption. The ``perfect prover" notion here is generalized and allows giving up.}
	then the verifier's output in the Hadamard round is $(\eps+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
\end{lemma}

@@

By Fact~\ref{fact:perfectly_pass_test} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda)$ probability.
\end{proof}

>>>>

\begin{lemma}[binding property of $\PiNaive$]
\label{lem:naive-qpip0-binding}
	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
	Under the QLWE assumption, if conditioned on $\PNaiveStar$ not aborting, $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
	\Ethan{Wrong assumption. The ``perfect prover" notion here is generalized and allows giving up.}
	then the verifier's output in the Hadamard round is $(\eps+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
\end{lemma}

@@

By Fact~\ref{fact:perfectly_pass_test} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda))$ probability. Therefore by Lemma~\ref{lem:urmila-binding}, there exist a state $\rho_{alt}$ such that 
\begin{align}
    z_{commit,alt} \approx~{c,\eps} M_{XZ}(\rho_{alt},h)
\end{align}
